Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-23 LaTeX_paper/paper.tex
format sections

\begin{abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for ``digital''~\cref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
the ``real world' jigsaw puzzle, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

@@

\section{The Objective Of This Paper}\label{document:objective}
After a review of the existing literature on this problem, some conclusions could be drawn:
The ``digital'' jigsaw puzzle dilemma has been extensively addressed and is already
well-optimized. Conversely, the ``real-world'' counterpart has largely been
overlooked within the academic community.

>>>>

\begin{abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for ``digital''~\cref{fig:figure_digital_puzzle} jigsaw puzzles. However, the counterpart:
the ``real world'' jigsaw puzzle~\cref{fig:figure_real_puzzle}, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

@@

\subsection{The Objective Of This Paper}\label{document:objective}
After a review of the existing literature on this problem, some conclusions could be drawn:
The ``digital'' jigsaw puzzle dilemma has been extensively addressed and is already
well-optimized. Conversely, the ``real-world'' counterpart has largely been
overlooked within the academic community.
